% !TEX root = SystemTemplate.tex

\chapter{Sprint Reports}

\section{Sprint Report \#1}

Product Owner: Charles Parsons,
Scrum Master: Christopher Smith,
Technical Lead: Jarod Hogan



What got done:
The first iteration of the testing suite was completed during spring 1. The program was able to take in a command line argument for the cpp file that was to be run against test files. We were able to get it to compile a program and run it against test files. After the program ran against test files the output files generated were than run through a diff command through the system call and compared. The program wrote pass or fail for the tst file depending on what was returned from the diff command. These results were written to a log file that was stored in the directory that the cpp file was found in.

What went well:
We were able to work together fairly well. The program did not take that long to write.

Problems Encountered:
We started working on the program to late so that the documentation was not done correctly. Also we forget to put the time in the file name when we logged the results so that it was not overwritten. Starting to late was the problem that made us encounter every other problem in getting sprint one completed.


\section{Sprint Report \#2}

Product Owner: Charles Parsons,
Scrum Master: Chris Smith,
Technical Lead: Jarod Hogan


What got done:
In this sprint we added an automatic test generation feature for floats and ints. The project also now processes an entire class by traversing sub-directories looking for cpp files and then compiling them. Critical tests were also introduced, these tests must all be passed before running any other tests. If any critical test is failed then the program gets a grade of “FAILED.” All of the results from critical tests, and other tests if run, are logged in the student's log file. The student's final grade is added as an entry in the class summary log file.

What went well:
We did a better job of dividing the work load for this sprint. We fulfilled all of the requirements, as we understood them. We worked well together to get this project completed.

Problems:
We did not have any problems that were more than momentary.

\section{Sprint Report \#3}
