% !TEX root = SystemTemplate.tex


\chapter{Project Overview}


\section{Team Members and Roles}
Charles Parsons - Product Owner
\\Jarod Hogan - Scrum Master
\\Chris Smith - Technical Lead


\section{Project  Management Approach}
The management approach we are taking with this project is Agile Scrum. We are using a 
Trello board to keep track of the product backlog, sprint backlog, sprint tasks, and user stories.


\section{Phase  Overview}
The first phase of the testing suite will accept a C++ source file and search the current
directory, as well as all sub-directories, for test case files that end in ".tst". The test suite
will then compile the source code and run the executable with the given ".tst" files as input. Program
output will be compared to corresponding answer (".ans") files and the results will be written to a 
log file in the root directory.
\\\\In the second phase, the test will be expanded all student C++ source files in the sub-directories
of the root class directory (ie CSC150). A main log file will be generated to report the grade of every student in the class. Individual student log files will report the students' results on individual test files. The program also has the capability to create test cases and corresponding answer files for future program tests.
\\\\In the third phase, many new features have been added. The test case generator in Sprint 2 has been expanded to include string test cases as well. Code coverage and performance testing have been added so the user may easily determine how thorough the test suite has tested the code. The ability to handle programs which run indefinitely has been added along with a timer set by the user to create a limit for each program. Finally, there has been added the ability to test menu driven programs and account for minor errors in presentation. 


\section{Terminology and Acronyms}
Section intentionally left blank.
